The title

### 2022-10-31 paper/manuscript.tex
update results (analysis, floating points)
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

The authors made the following contributions. Atsuko Tominaga: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Günther Knoblich: Writing - Review \& Editing, Supervision; Natalie Sebanz: Writing - Review \& Editing, Supervision.

@@

\abstract{%
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

@@

The experiment was programmed in Max/MSP (8.1.11; \url{https://cycling74.com/products/max}) on a Mac Book Pro with Mac OS X Catalina 10.15.7. A weighted Yamaha MIDI digital piano was used to record participants' performance. The pitch, onset and offset time of each note, and key velocity profiles were obtained from MIDI data using Max/MSP patchers. All auditory feedback was given to participants through headphones (Audio-Technica ATH-M50X). Sheet music was displayed on a computer monitor in front of the participants.

@@

Neither main effect of Articulation (\emph{F}(1, 19) = 2.79, \emph{p} = 0.11, \(\eta_G^2\) = 0.010) and Dynamics (\emph{F}(1, 19) = 3.27, \emph{p} = 0.09, \(\eta_G^2\) = 0.003) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 1.48, \emph{p} = 0.24, \(\eta_G^2\) = 0.002). Therefore, participants did not change the tempo depending on the types of the recordings (\emph{Fig \ref{fig:ioi-1}}).

@@

There was a significant main effect of Articulation (\emph{F}(1, 19) = 5.59, \emph{p} = 0.03, \(\eta_G^2\) = 0.002). However, there was no significant main effect of Dynamics (\emph{F}(1, 19) = 0.06, \emph{p} = 0.81, \(\eta_G^2\) = 0.000) or interaction between Articulation and Dynamics (\emph{F}(1, 19) = 1.89, \emph{p} = 0.19, \(\eta_G^2\) = 0.002). Participants produced longer legato when listening to the recordings where articulation was not implemented (\emph{Fig \ref{fig:kot-1}}, left).

@@

There was a significant main effect of Articulation (\emph{F}(1, 19) = 4.88, \emph{p} = 0.04, \(\eta_G^2\) = 0.009). However, there was no significant main effect of Dynamics (\emph{F}(1, 19) = 0.68, \emph{p} = 0.42, \(\eta_G^2\) = 0.000) or interaction between Articulation and Dynamics (\emph{F}(1, 19) = 3.13, \emph{p} = 0.09, \(\eta_G^2\) = 0.001). Participants produced shorter staccato when listening to the recordings where articulation was not implemented (\emph{Fig \ref{fig:kot-1}}, right).

@@

Neither main effect of Articulation (\emph{F}(1, 19) = 1.66, \emph{p} = 0.21, \(\eta_G^2\) = 0.002) and Dynamics (\emph{F}(1, 19) = 0.33, \emph{p} = 0.57, \(\eta_G^2\) = 0.000) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 0.00, \emph{p} = 0.96, \(\eta_G^2\) = 0.000). Participants did not change performances in terms of dynamics (loudness) depending on the types of the recordings (\emph{Fig \ref{fig:vel-1}}, left).

@@

Neither main effect of Articulation (\emph{F}(1, 19) = 3.40, \emph{p} = 0.08, \(\eta_G^2\) = 0.012) and Dynamics (\emph{F}(1, 19) = 1.58, \emph{p} = 0.22, \(\eta_G^2\) = 0.002) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 0.97, \emph{p} = 0.34, \(\eta_G^2\) = 0.001).

@@

Neither main effect of Articulation (\emph{F}(1, 19) = 2.25, \emph{p} = 0.15, \(\eta_G^2\) = 0.005) and Dynamics (\emph{F}(1, 19) = 3.76, \emph{p} = 0.07, \(\eta_G^2\) = 0.004) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 1.08, \emph{p} = 0.31, \(\eta_G^2\) = 0.001).

@@

There was no significant main effect of Category (\emph{F}(1.11, 21.18) = 0.58, \emph{p} = 0.47, \(\eta_G^2\) = 0.012; Greenhouse--Geisser corrected), suggesting that participants kept the tempo regardless of whether they had an intention to teach (\emph{Fig \ref{fig:ioi-2}}).

@@

There was a significant main effect of Category (\emph{F}(1.45, 27.53) = 11.82, \emph{p} = 0.00, \(\eta_G^2\) = 0.060; Greenhouse--Geisser corrected). Post-hoc comparisons based on the estimated marginal means with Tukey adjustment showed that there were differences between baseline and the other two categories (baseline and both: \emph{p} \textless{} .001 , baseline and dynamics-only: \emph{p} = .008), suggesting that participants produced longer legato when they had an intention to teach (\emph{Fig \ref{fig:kot-2}}, left).

@@

There was no significant main effect of Category (\emph{F}(1.12, 21.28) = 0.75, \emph{p} = 0.41, \(\eta_G^2\) = 0.011; Greenhouse--Geisser corrected), suggesting that participants did not play staccato differently depending on whether they had an intention to teach (\emph{Fig \ref{fig:kot-2}}, right).

@@

There was no significant main effect of Category (\emph{F}(1.59, 30.18) = 1.43, \emph{p} = 0.25, \(\eta_G^2\) = 0.004; Greenhouse--Geisser corrected), suggesting that participants did not play forte differently depending on whether they had an intention to teach (\emph{Fig \ref{fig:vel-2}}, left).

@@

There was a significant main effect of Category (\emph{F}(1.79, 34.09) = 5.68, \emph{p} = 0.01, \(\eta_G^2\) = 0.072; Greenhouse--Geisser corrected). Post-hoc comparisons based on the estimated marginal means with Tukey adjustment showed that there were differences between baseline and the other two categories (baseline and both: \emph{p} = .05 , baseline and articulation-only: \emph{p} = .03), suggesting that participants produced softer piano when they had an intention to teach (\emph{Fig \ref{fig:vel-2}}, right).

@@

There was no significant main effect of Category (\emph{F}(1.53, 29.15) = 1.73, \emph{p} = 0.20, \(\eta_G^2\) = 0.014; Greenhouse--Geisser corrected).

@@

There was no significant main effect of Category (\emph{F}(1.28, 24.39) = 2.27, \emph{p} = 0.14, \(\eta_G^2\) = 0.013; Greenhouse--Geisser corrected).

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-ioi-2-1} \caption{\label{fig:ioi-2}Comaprison with the baseline performance in terms of IOIs (ms). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-ioi-2}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-kot-2-1} \caption{\label{fig:kot-2}Comaprison with the baseline performance in terms of KOT(ms) for each subcomponent; legato (left) and staccato (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-kot-2}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-vel-2-1} \caption{\label{fig:vel-2}Comaprison with the baseline performance in terms of KV (0-127) for each subcomponent; forte (left) and piano (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-vel-2}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-vel-diff-2-1} \caption{\label{fig:vel-diff-2}Comaprison with the baseline performance in terms of KV Difference (-127-127) for each subcomponent; forte to piano (left) and piano to forte (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-vel-diff-2}
\end{figure}

@@

>>>>

@@

\abstract{%
AAA
}

@@

The experiment was programmed in Max/MSP (8.1.11; \url{https://cycling74.com/products/max}) on a Mac Book Pro with Mac OS X Catalina 10.15.7. A weighted Yamaha MIDI digital piano was used to record participants' performances. The pitch, onset and offset time of each note, and key velocity profiles were obtained from MIDI data using Max/MSP patchers. All auditory feedback was given to participants through headphones (Audio-Technica ATH-M50X). Sheet music was displayed on a computer monitor in front of the participants.

@@

Neither main effect of Articulation (\emph{F}(1, 19) = 2.79, \emph{p} = 0.111, \(\eta_G^2\) = 0.010) or Dynamics (\emph{F}(1, 19) = 3.27, \emph{p} = 0.086, \(\eta_G^2\) = 0.003) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 1.48, \emph{p} = 0.24, \(\eta_G^2\) = 0.002). Therefore, participants did not change the tempo depending on the types of the recordings (\emph{Fig \ref{fig:ioi-1}}).

@@

There was a significant main effect of Articulation (\emph{F}(1, 19) = 5.59, \emph{p} = 0.029, \(\eta_G^2\) = 0.002). However, there was no significant main effect of Dynamics (\emph{F}(1, 19) = 0.06, \emph{p} = 0.81, \(\eta_G^2\) = 0.000) or interaction between Articulation and Dynamics (\emph{F}(1, 19) = 1.89, \emph{p} = 0.19, \(\eta_G^2\) = 0.002). Participants produced longer legato when listening to the recordings where articulation was not implemented (\emph{Fig \ref{fig:kot-1}}, left).

@@

There was a significant main effect of Articulation (\emph{F}(1, 19) = 4.88, \emph{p} = 0.040, \(\eta_G^2\) = 0.009). However, there was no significant main effect of Dynamics (\emph{F}(1, 19) = 0.68, \emph{p} = 0.42, \(\eta_G^2\) = 0.000) or interaction between Articulation and Dynamics (\emph{F}(1, 19) = 3.13, \emph{p} = 0.093, \(\eta_G^2\) = 0.001). Participants produced shorter staccato when listening to the recordings where articulation was not implemented (\emph{Fig \ref{fig:kot-1}}, right).

@@

Neither main effect of Articulation (\emph{F}(1, 19) = 1.66, \emph{p} = 0.213, \(\eta_G^2\) = 0.00) or Dynamics (\emph{F}(1, 19) = 0.33, \emph{p} = 0.57, \(\eta_G^2\) = 0.000) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 0.00, \emph{p} = 0.96, \(\eta_G^2\) = 0.000). Participants did not change performances in terms of dynamics (loudness) depending on the types of the recordings (\emph{Fig \ref{fig:vel-1}}, left).

@@

Neither main effect of Articulation (\emph{F}(1, 19) = 3.40, \emph{p} = 0.081, \(\eta_G^2\) = 0.012) or Dynamics (\emph{F}(1, 19) = 1.58, \emph{p} = 0.22, \(\eta_G^2\) = 0.002) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 0.97, \emph{p} = 0.336, \(\eta_G^2\) = 0.001).

@@

Neither main effect of Articulation (\emph{F}(1, 19) = 2.25, \emph{p} = 0.150, \(\eta_G^2\) = 0.005) or Dynamics (\emph{F}(1, 19) = 3.76, \emph{p} = 0.07, \(\eta_G^2\) = 0.004) nor the interaction between Articulation and Dynamics was significant (\emph{F}(1, 19) = 1.08, \emph{p} = 0.31, \(\eta_G^2\) = 0.001).

@@

There was no significant main effect of Category (\emph{F}(1.11, 21.18) = 0.58, \emph{p} = 0.47, \(\eta_G^2\) = 0.012; Greenhouse-Geisser corrected), suggesting that participants kept the same tempo regardless of whether they had an intention to teach (\emph{Fig \ref{fig:ioi-2}}).

@@

There was a significant main effect of Category (\emph{F}(1.45, 27.53) = 11.82, \emph{p} \textless{} 0.001, \(\eta_G^2\) = 0.060; Greenhouse-Geisser corrected). Post-hoc comparisons based on the estimated marginal means with Tukey adjustment showed that there were differences between baseline and the other two categories (baseline and both: \emph{p} \textless{} .001 , baseline and dynamics-only: \emph{p} .008), suggesting that participants produced longer legato when they had an intention to teach (\emph{Fig \ref{fig:kot-2}}, left).

@@

There was no significant main effect of Category (\emph{F}(1.12, 21.28) = 0.75, \emph{p} = 0.41, \(\eta_G^2\) = 0.011; Greenhouse-Geisser corrected), suggesting that participants did not play staccato differently depending on whether they had an intention to teach (\emph{Fig \ref{fig:kot-2}}, right).

@@

There was no significant main effect of Category (\emph{F}(1.59, 30.18) = 1.43, \emph{p} = 0.25, \(\eta_G^2\) = 0.004; Greenhouse-Geisser corrected), suggesting that participants did not play forte differently depending on whether they had an intention to teach (\emph{Fig \ref{fig:vel-2}}, left).

@@

There was a significant main effect of Category (\emph{F}(1.79, 34.09) = 5.68, \emph{p} = 0.009, \(\eta_G^2\) = 0.072; Greenhouse-Geisser corrected). Post-hoc comparisons based on the estimated marginal means with Tukey adjustment showed that there were differences between baseline and the other two categories (baseline and both: \emph{p} .05 , baseline and articulation-only: \emph{p} .03), suggesting that participants produced softer piano when they had an intention to teach (\emph{Fig \ref{fig:vel-2}}, right).

@@

There was no significant main effect of Category (\emph{F}(1.53, 29.15) = 1.73, \emph{p} = 0.20, \(\eta_G^2\) = 0.014; Greenhouse-Geisser corrected).

@@

There was no significant main effect of Category (\emph{F}(1.28, 24.39) = 2.27, \emph{p} = 0.14, \(\eta_G^2\) = 0.013; Greenhouse-Geisser corrected).

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-ioi-2-1} \caption{\label{fig:ioi-2}Comparison with the baseline performance in terms of IOIs (ms). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-ioi-2}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-kot-2-1} \caption{\label{fig:kot-2}Comparison with the baseline performance in terms of KOT(ms) for each subcomponent; legato (left) and staccato (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-kot-2}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-vel-2-1} \caption{\label{fig:vel-2}Comparison with the baseline performance in terms of KV (0-127) for each subcomponent; forte (left) and piano (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-vel-2}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-vel-diff-2-1} \caption{\label{fig:vel-diff-2}Comparison with the baseline performance in terms of KV Difference (-127-127) for each subcomponent; forte to piano (left) and piano to forte (right). Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-vel-diff-2}
\end{figure}

@@

The present study investigated whether and how expert pianists adapt their performance depending on the skill levels of students. We manipulated the implementation of articulation and dynamics in the piece to create four types of artificial recordings. These recordings were supposed to be the reflection of students' skill levels. In one quarter of the recordings, both articulation and dynamics were implemented
{[}SUMMARY{]}.
We found that
Limitation
